---
title: RT analyses
author: Hannah, 6/22/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=140)
require(dplyr)
require(ggplot2)
require(lme4)
require(lmerTest)
```

**Major changes: Updated plots to add CIs**

Uses RT data from Alc Caf for condition 4 (Placebo-placebo) and condition 5 (Control).

“Current” trial will be included if:  
1) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
2) Both current trial and previous trial are correct.  
3) RT is longer than 200 ms and shorter than 2000 ms.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  

Each subject did 800 trials, with 100 trials in each of 8 blocks.

**Total sample is 50 subjects.**


```{r data, echo = FALSE}
dat = read.delim("FlankerRT_forR.txt")
dat = dat[dat$ACC == 1 & dat$PrevTrialACC == 1,]

# discard trials for which RT is less than 100 and greater than 2000
dat$RTdrop = dat$RT_Raw
dat$RTdrop[dat$RT_Raw < 100] = NA
dat$RTdrop[dat$RT_Raw > 2000] = NA

# add trial information
dat$prevTrialType = NA
dat$prevTrialType[dat$PrevTrialType == 1] = "compatible"
dat$prevTrialType[dat$PrevTrialType == 2] = "incompatible"
dat$prevTrialType = factor(dat$prevTrialType)

# select subjects in Condition 4 and 5, take out 92 and 64
dat.use = dat[dat$Condition == 4|dat$Condition == 5,] %>% 
  filter(Subject != 92) %>% 
  filter(Subject != 64)

dat.use$Condition = paste(dat.use$prevTrialType, dat.use$TrialType, sep="_")

tapply(dat.use$RTdrop100_2000, dat.use$TrialType, mean)
tapply(dat.use$RTdrop100_2000, dat.use$Condition, mean)

```

### 1. Gratton effect at experiment level (grand averages)

```{r plotGratton, echo=FALSE}
# estimate model (dummy code) to find marginal means-- doesn't include trial
plot1 = lmer(RTdrop ~ TrialType*prevTrialType + (TrialType+prevTrialType|Subject), data = dat.use)

parms <- fixef(plot1) # fixed parameters from model
vcmat <- vcov(plot1) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,4)
Tmat[1,] <- c(1,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2) +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  ggtitle("Reaction Time")+
  coord_cartesian(ylim = c(350, 450)) +
  scale_color_manual(values=c(1, 2), guide = guide_legend(title = "Current trial")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

ggsave("./Figures/Figure4a.tiff", width= 6, height= 7)
```
  
This plot shows marginal means and 95% CI from the (dummy coded) model.   
To look at the fixed effects, current trial type and previous trial type are effect coded.
  
``` {r testGratton, echo=FALSE}
# make effect coding variables
dat.use$Current.e = NA
dat.use$Current.e[dat.use$TrialType == "compatible"] = -1
dat.use$Current.e[dat.use$TrialType == "Incompatible"] = 1

dat.use$Previous.e = NA
dat.use$Previous.e[dat.use$prevTrialType == "compatible"] = -1
dat.use$Previous.e[dat.use$prevTrialType == "incompatible"] = 1

# add label for trial condition
dat.use$TrialCondition = "Previous compatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "compatible" & dat.use$TrialType == "compatible"] = 
  "Previous compatible - Current compatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "Incompatible"] = 
  "Previous incompatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "compatible"] = 
  "Previous incompatible - Current compatible"
dat.use$TrialCondition = factor(dat.use$TrialCondition)

# now estimate model again (without trial) but with effect coded variables
m1 = lmer(RTdrop ~ Current.e*Previous.e + (Current.e*Previous.e|Subject), data = dat.use) 

```
  
**Random effects:**  
``` {r model1random, echo = FALSE}
summary(m1)$varcor
```

**Fixed effects:**
``` {r model1fixed, echo = FALSE} 
round(summary(m1)$coefficients, digits = 3)
```

Significant interaction between current trial and previous trial indicates the presence of the Gratton effect. 


### 2. Looking at change over course of task  
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r trialLevel, echo = FALSE, warning = FALSE}
# data set up in 8 blocks, trial goes 1-100 in each block
# add column for trial number across whole experiment so it goes 1-800
dat.use$ExpTrial = dat.use$Trial + (100*(dat.use$Block - 1))

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
plot1.d <- lmer(RTdrop ~ TrialType*prevTrialType*ExpTrial + (TrialType+prevTrialType|Subject), data = dat.use)

parms <- fixef(plot1.d) # fixed parameters from model
vcmat <- vcov(plot1.d) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("cC", "iC", "cI", "iI")

# make separate matrices for weights to calc SES for each condition
numTrials = 800
numFixed = 8 # refers to the number of rows in the fixed effects (intercept, previous, current, trial, interactions, etc.)
numConditions = 4

# cC
cC.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
cC.SE[,1] = 1 # first column is intercept
cC.SE[,2] = 0 # second column is current 
cC.SE[,3] = 0 # third column is previous
cC.SE[,4] = 1:numTrials # fourth column is trial
cC.SE[,5] = 0 # fifth column is current*previous
cC.SE[,6] = 0 # sixth column is current*trial
cC.SE[,7] = 0 # seventh column is previous*trial
cC.SE[,8] = 0 # eighth column is current*previous*trial

# cI
cI.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
cI.SE[,1] = 1 # first column is intercept
cI.SE[,2] = 1 # second column is current 
cI.SE[,3] = 0 # third column is previous
cI.SE[,4] = 1:numTrials # fourth column is trial
cI.SE[,5] = 0 # fifth column is current*previous
cI.SE[,6] = 1:numTrials # sixth column is current*trial
cI.SE[,7] = 0 # seventh column is previous*trial
cI.SE[,8] = 0 # eighth column is current*previous*trial

# iC
iC.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
iC.SE[,1] = 1 # first column is intercept
iC.SE[,2] = 0 # second column is current 
iC.SE[,3] = 1 # third column is previous
iC.SE[,4] = 1:numTrials # fourth column is trial
iC.SE[,5] = 0 # fifth column is current*previous
iC.SE[,6] = 0 # sixth column is current*trial
iC.SE[,7] = 1:numTrials # seventh column is previous*trial
iC.SE[,8] = 0 # eighth column is current*previous*trial

# iI
iI.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
iI.SE[,1] = 1 # first column is intercept
iI.SE[,2] = 1 # second column is current 
iI.SE[,3] = 1 # third column is previous
iI.SE[,4] = 1:numTrials # fourth column is trial
iI.SE[,5] = 1 # fifth column is current*previous
iI.SE[,6] = 1:numTrials # sixth column is current*trial
iI.SE[,7] = 1:numTrials # seventh column is previous*trial
iI.SE[,8] = 1:numTrials # eighth column is current*previous*trial

SETmat = rbind(cC.SE, iC.SE, cI.SE, iI.SE)
newvc <- SETmat %*% vcmat %*% t(SETmat)
ses <- sqrt(diag(newvc)) # long string of SEs for each trial, conditions and rows are long

SE.dat = data.frame(Condition = rep(c("cC", "iC", "cI", "iI"), each=numTrials), Trial = rep(c(1:numTrials), numConditions), SE = ses)

# sloppy, and there's probably a better way of doing this
# but take slope and intercept and calculate all the points on the line for each trial so that I can calculate upper and lower 95% CIs 
SE.dat$Point = NULL
for (i in c("cC", "iC", "cI", "iI")){
  SE.dat$Point[SE.dat$Condition == i] = forPlotting$Intercept[forPlotting$TrialCondition == i] + 1:numTrials*forPlotting$Slope[forPlotting$TrialCondition == i]
}

# calculate upper and lower bound (+/- 1 SE)
SE.dat$upper = SE.dat$Point + SE.dat$SE
SE.dat$lower = SE.dat$Point - SE.dat$SE

ggplot(SE.dat, aes(Trial, Point, group = Condition)) +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, x = Trial), alpha = 0, linetype = "dashed", color = "black")

# BINGO -------------------------------------------------------------------
ggplot(SE.dat, aes(Trial, Point, group = Condition)) +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color=TrialCondition, linetype=TrialCondition),
              size = 1)+
  geom_ribbon(aes(ymin=lower, ymax=upper, x = Trial, color = Condition),
              linetype = "dotted",
              alpha = .1) +
  labs(x = "Trial", y = "Reaction Time (ms)") +
  #scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  scale_y_continuous(limits =c(325, 500), expand=c(0,0)) +
  scale_x_continuous(expand=c(0,0), breaks=c(0, 100, 200, 300, 400, 500, 600, 700, 800)) + 
#  ggtitle("Plotted with estimates from MLM") +  
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))


ggsave("./Figures/Figure1.tiff", width = 7, height = 5)
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r simple, echo = FALSE}
# rescale trial
dat.use$Trial.begin = (dat.use$ExpTrial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
dat.use$Trial.middle = dat.use$Trial.begin - 4
dat.use$Trial.end = dat.use$Trial.begin - 8

# find slopes with dummy coded model, trial is scaled
begin.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.begin + (TrialType+prevTrialType|Subject), data = dat.use)

parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("blue dashed", "red dashed", "blue solid", "red solid")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
fin
```  

#### Beginning of experiment
The intercept, slopes of current and previous trial condition and their interaction are allowed to vary by subject. The same random effects structure is used to probe effects at the beginning, middle, and end of the experiment. *Categorical variables are effect coded.*   
  
To probe effects at the beginning of the experiment, trial is scaled to range from 0 to 8.  

``` {r begin, echo = FALSE}
# same model, but with effect coding
begin.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.begin + (Current.e*Previous.e|Subject), data = dat.use)
```
  
**Random effects:**  
``` {r beginrandom, echo = FALSE}
summary(begin.e)$varcor
```

**Fixed effects:**
``` {r beginfixed, echo = FALSE} 
round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3)
round(summary(begin.e)$coefficients[c(4,6:8),1:5], digits = 3)
```

**Marginal means:**  
Error bars represent standard error.  
``` {r beginmarginal, echo = FALSE}
# basically we're calculating intercepts (marginal means) instead of slopes, which we did earlier

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plotting
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)

condColors = c("forestgreen", "Black")
condLinetype = c("dashed", "solid")

ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  theme_bw() +
  ggtitle("Beginning") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

  
```

#### Middle of experiment 
To probe effects at the middle of the experiment, trial is shifted so that trial ranges from -4 to 4.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*  

**Fixed effects:**
``` {r middle, echo = FALSE}

middle.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.middle + (Current.e*Previous.e|Subject), data = dat.use)

round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 4)
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r middlemarginal, echo = FALSE}
# use dummy coded model
middle.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.middle + (TrialType+prevTrialType|Subject), data = dat.use)
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  theme_bw() +
  ggtitle("Middle") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```

#### End of experiment 
To probe the effects at the end of the experiment, trial is shifted so that trial ranges from -8 to 0.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*
  
**Fixed effects:**  
``` {r end, echo = FALSE}
end.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.end + (Current.e*Previous.e|Subject), data = dat.use)

round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 4)
```
**Marginal means:**  
Error bars represent standard error.  
``` {r endmarginal, echo = FALSE}
# use dummy coded model
end.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.end + (TrialType+prevTrialType|Subject), data = dat.use)
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  theme_bw() +
  ggtitle("End") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```
