---
title: N2analyses
author: Hannah, 7/9/17
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=140)
require(dplyr)
require(lme4)
require(lmerTest)
require(ggplot2)
```

**Major changes: Updated plot of change over time to get rid of points and include CIs.**

Curt reprocessed the data using an automatic artifact rejection process with +- 75 uV as the threshold for rejection. He quantified the N2 for each trial between [put N2 interval here]. I selected the trials that fit these criteria:

“Current” trial will be included if:  
1) Current trial is not rejected due to artifacts.  
2) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
3) Both current trial and previous trial are correct.  

The following electrodes are included: F3, Fz, F4, FC3, FCz, FC4, C3, Cz, C4.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  
- 65 (only 187 usable trials (23.3%))

One or more electrodes were bad for subjects 19, 74, and 137 (data from those electrodes is discarded).  

Besides that, ERP data is completely missing for subs 36, 37, 39, 40, 42, 43, 46, 51, 53, 54, 56, 57, 78.
  
**Total sample is 36 subjects.**

### 1. Grand averages, not looking at change over experiment

``` {r plotGrand, echo=FALSE, warning=F}
N2.correct = read.delim("./AllSubs_TBTaverages_N2_Correct_withPrevious_EventFixed.txt")

tapply(N2.correct$MeanCurr, N2.correct$Condition, mean, na.rm=T)
tapply(N2.correct$MeanCurr, N2.correct$Condition, sd, na.rm=T)
tapply(N2.correct$MeanCurr, N2.correct$prevCond, mean, na.rm=T)
```

Average number of trials in each condition for each subject:
``` {r}
data.frame(iC = nrow(filter(N2.correct, TrialCondition == "Previous incompatible - Current compatible"))/36/9,
           cC = nrow(filter(N2.correct, TrialCondition == "Previous compatible - Current compatible"))/36/9,
           cI = nrow(filter(N2.correct, TrialCondition == "Previous compatible - Current incompatible"))/36/9,
           iI = nrow(filter(N2.correct, TrialCondition == "Previous incompatible - Current incompatible"))/36/9)

# estimate model (dummy code) to find marginal means-- doesn't include trial
plot1 = lmer(MeanCurr ~ Condition*prevCond + (Condition+prevCond|Subject), data = N2.correct)

parms <- fixef(plot1) # fixed parameters from model
vcmat <- vcov(plot1) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,4)
Tmat[1,] <- c(1,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2) +
  scale_color_manual(values=c(1, 2), guide = guide_legend(title = "Current trial")) +
  ylab("Mean Amplitude (uV)") +
  xlab("Previous Trial") +
  ggtitle("N2")+
  coord_cartesian(ylim = c(1.1, 3.1)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

ggsave("./Figures/Figure4b.tiff", width= 6, height= 7)

```
  
*Current and Previous are effect coded.* Uses trial-level data to test (rather than individual averages). Doesn't include Trial in model. 

``` {r test, echo=FALSE}
# to run model

# add effect codes for categorical variables
N2.correct$Previous = NA
N2.correct$Previous[N2.correct$prevCond == "compat"] = -1
N2.correct$Previous[N2.correct$prevCond == "incompat"] = 1

N2.correct$Current = NA
N2.correct$Current[N2.correct$Condition == "Comp"] = -1
N2.correct$Current[N2.correct$Condition == "InComp"] = 1

grand1 = lmer(MeanCurr ~ Current*Previous + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = N2.correct)

```
  
**Random effects:**  
``` {r grand1random, echo = FALSE}
summary(grand1)$varcor
```

**Fixed effects:**
``` {r grand1fixed, echo = FALSE} 
round(summary(grand1)$coefficients, digits = 3)
```

### 2. Looking at change over course of task  
**This includes all data points, *not* averaged across subject or electrode.** 

```{r plot, echo=FALSE, warning = FALSE}
# calculate simple slopes
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = N2.correct)

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("cC", "iC", "cI", "iI")

# make separate matrices for weights to calc SES for each condition
numTrials = 800
numFixed = 8 # refers to the number of rows in the fixed effects (intercept, previous, current, trial, interactions, etc.)
numConditions = 4

# cC
cC.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
cC.SE[,1] = 1 # first column is intercept
cC.SE[,2] = 0 # second column is current 
cC.SE[,3] = 0 # third column is previous
cC.SE[,4] = 1:numTrials # fourth column is trial
cC.SE[,5] = 0 # fifth column is current*previous
cC.SE[,6] = 0 # sixth column is current*trial
cC.SE[,7] = 0 # seventh column is previous*trial
cC.SE[,8] = 0 # eighth column is current*previous*trial

# cI
cI.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
cI.SE[,1] = 1 # first column is intercept
cI.SE[,2] = 1 # second column is current 
cI.SE[,3] = 0 # third column is previous
cI.SE[,4] = 1:numTrials # fourth column is trial
cI.SE[,5] = 0 # fifth column is current*previous
cI.SE[,6] = 1:numTrials # sixth column is current*trial
cI.SE[,7] = 0 # seventh column is previous*trial
cI.SE[,8] = 0 # eighth column is current*previous*trial

# iC
iC.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
iC.SE[,1] = 1 # first column is intercept
iC.SE[,2] = 0 # second column is current 
iC.SE[,3] = 1 # third column is previous
iC.SE[,4] = 1:numTrials # fourth column is trial
iC.SE[,5] = 0 # fifth column is current*previous
iC.SE[,6] = 0 # sixth column is current*trial
iC.SE[,7] = 1:numTrials # seventh column is previous*trial
iC.SE[,8] = 0 # eighth column is current*previous*trial

# iI
iI.SE <- matrix(NA,numTrials,numFixed) # matrix will have numTrials rows and numFixed columns. Here, that's 800 rows and 8 columns
iI.SE[,1] = 1 # first column is intercept
iI.SE[,2] = 1 # second column is current 
iI.SE[,3] = 1 # third column is previous
iI.SE[,4] = 1:numTrials # fourth column is trial
iI.SE[,5] = 1 # fifth column is current*previous
iI.SE[,6] = 1:numTrials # sixth column is current*trial
iI.SE[,7] = 1:numTrials # seventh column is previous*trial
iI.SE[,8] = 1:numTrials # eighth column is current*previous*trial

SETmat = rbind(cC.SE, iC.SE, cI.SE, iI.SE)
newvc <- SETmat %*% vcmat %*% t(SETmat)
ses <- sqrt(diag(newvc)) # long string of SEs for each trial, conditions and rows are long

SE.dat = data.frame(Condition = rep(c("cC", "iC", "cI", "iI"), each=numTrials), Trial = rep(c(1:numTrials), numConditions), SE = ses)

# sloppy, and there's probably a better way of doing this
# but take slope and intercept and calculate all the points on the line for each trial so that I can calculate upper and lower 95% CIs 
SE.dat$Point = NULL
for (i in c("cC", "iC", "cI", "iI")){
  SE.dat$Point[SE.dat$Condition == i] = forPlotting$Intercept[forPlotting$TrialCondition == i] + 1:numTrials*forPlotting$Slope[forPlotting$TrialCondition == i]
}

# calculate upper and lower bound (+/- 1 SE)
SE.dat$upper = SE.dat$Point + SE.dat$SE
SE.dat$lower = SE.dat$Point - SE.dat$SE

# Revised plot- BINGO
ggplot(SE.dat, aes(Trial, Point, group = Condition)) +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color=TrialCondition, linetype=TrialCondition),
              size = 1)+
  geom_ribbon(aes(ymin=lower, ymax=upper, x = Trial, color = Condition),
              linetype = "dotted",
              alpha = .1) +
  labs(x = "Trial", y = "N2 Amplitude (uV)") +
  #scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("navy", "navy", "magenta1", "magenta1")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  scale_y_continuous(limits =c(-1.7, 5), expand=c(0,0)) +
  scale_x_continuous(expand=c(0,0), breaks=c(0, 100, 200, 300, 400, 500, 600, 700, 800)) + 
#  ggtitle("Plotted with estimates from MLM") +  
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))


ggsave("./Figures/Figure2.tiff", width = 7, height = 5)


```
  
##### Simple slopes  
  
Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).   

``` {r simple, echo = FALSE}
# rescale trial
N2.correct$Trial.begin = (N2.correct$Trial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
N2.correct$Trial.middle = N2.correct$Trial.begin - 4
N2.correct$Trial.end = N2.correct$Trial.begin - 8

fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = N2.correct)

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("dark blue", "dark red", "light blue", "light red")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
fin
```  

  
#### Beginning of experiment 
The intercept and slopes of current and previous trial condition are allowed to vary by subject. The intercept is allowed to vary by electrode nested within subject.   
  
Trial is scaled to range from 0 to 8.  

Categorical variables are effect coded. 

``` {r model1, echo = FALSE}

m1 = lmer(MeanCurr ~ Current*Previous*Trial.begin + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = N2.correct)
```

**Random effects:**  
``` {r model1random, echo = FALSE}
summary(m1)$varcor
```

**Fixed effects:**
``` {r model1fixed, echo = FALSE} 
round(summary(m1)$coefficients[c(1:3,5),1:5], digits = 3)
round(summary(m1)$coefficients[c(4,6:8),1:5], digits = 3)
```

**Marginal means:**  
Error bars represent standard error.  
``` {r model1marginal, echo = FALSE}
# use dummy coded model
# was calculated earlier for simple slopes (fm2)
parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plotting
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)

condColors = c("forestgreen", "Black")
condLinetype = c("dashed", "solid")

ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("Beginning") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

  
```


#### Middle of experiment 
Trial is shifted so that trial ranges from -4 to 4.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*  

**Fixed effects:**
``` {r model2, echo = FALSE}
# effect
m2 = lmer(MeanCurr ~ Current*Previous*Trial.middle + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = N2.correct)

round(summary(m2)$coefficients[c(1:3,5),1:5], digits = 3)

```
**Marginal means:**  
Error bars represent standard error.  
``` {r model2marginal, echo = FALSE}
# use dummy coded model
fm3 <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = N2.correct)
parms <- fixef(fm3) # fixed parameters from model
vcmat <- vcov(fm3) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("Middle") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```


#### End of experiment 
Trial is shifted so that trial ranges from -8 to 0.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*
  
**Fixed effects:**
``` {r model3, echo = FALSE}
m3 = lmer(MeanCurr ~ Current*Previous*Trial.end + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = N2.correct)

round(summary(m3)$coefficients[c(1:3,5),1:5], digits = 3)
```
**Marginal means:**  
Error bars represent standard error.  
``` {r model3marginal, echo = FALSE}
# use dummy coded model
fm4 <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = N2.correct)
parms <- fixef(fm4) # fixed parameters from model
vcmat <- vcov(fm4) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plotting
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("End") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```

