---
title: SlowWaveanalyses
author: Curt, 2/3/2017; Hannah, 3/31/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=140)
require(dplyr)
require(lme4)
require(lmerTest)
require(ggplot2)
```


**Major changes: Reknitted with new data (trials fixed for subs 2, 4, 8, 16, 17, 19, 30, 59, 70, 72. Also, 74 and 19 were missing before, are now included.**

I reprocessed the data using an automatic artifact rejection process with +- 75 uV as the threshold for rejection. SlowWave was quantified between [put in time interval here]. I selected the trials that fit these criteria:

“Current” trial will be included if:  
1) Current trial is not rejected due to artifacts.  
2) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
3) Both current trial and previous trial are correct.  

The following electrodes are included: F3, Fz, F4, FC3, FCz, FC4, C3, Cz, C4.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  
- 65 (only 187 usable trials (23.3%))

One or more electrodes were bad for subjects 19, 74, and 137 (data from those electrodes is discarded).  

Besides that, ERP data is completely missing for subs 36, 37, 39, 40, 42, 43, 46, 51, 53, 54, 56, 57, 78.
  
**Total sample is 36 subjects.**  

### 1. Grand averages, not looking at change over experiment

``` {r plotGrand, echo=FALSE, warning=F}
SlowWave.correct = read.delim("AllSubs_TBTaverages_SlowWave_Correct_withPrevious_EventFixed.txt")

tapply(SlowWave.correct$MeanCurr, SlowWave.correct$Condition, mean, na.rm=T)

# estimate model (dummy code) to find marginal means-- doesn't include trial
plot1 = lmer(MeanCurr ~ Condition*prevCond + (Condition+prevCond|Subject), data = SlowWave.correct)

parms <- fixef(plot1) # fixed parameters from model
vcmat <- vcov(plot1) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,4)
Tmat[1,] <- c(1,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2) +
  scale_color_manual(values=c(1, 2), guide = guide_legend(title = "Current trial")) +
  ylab("Mean Amplitude (uV)") +
  xlab("Previous Trial") +
  ggtitle("FSW")+
  coord_cartesian(ylim = c(-3, -1)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

ggsave("./Figures/Figure4c.tiff", width= 6, height= 7)
```
  
*Current and Previous are effect coded.* Uses trial-level data to test (rather than individual averages). Doesn't include Trial in model. 

``` {r test, echo=FALSE}
# to run model

# add effect codes for categorical variables
SlowWave.correct$Previous = NA
SlowWave.correct$Previous[SlowWave.correct$prevCond == "compat"] = -1
SlowWave.correct$Previous[SlowWave.correct$prevCond == "incompat"] = 1

SlowWave.correct$Current = NA
SlowWave.correct$Current[SlowWave.correct$Condition == "Comp"] = -1
SlowWave.correct$Current[SlowWave.correct$Condition == "InComp"] = 1

grand1 = lmer(MeanCurr ~ Current*Previous + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

```
  
**Random effects:**  
``` {r grand1random, echo = FALSE}
summary(grand1)$varcor
```

**Fixed effects:**
``` {r grand1fixed, echo = FALSE} 
round(summary(grand1)$coefficients, digits = 3)
```

### 2. Looking at change over course of task  
**This includes all data points, *not* averaged across subject or electrode.**  

```{r plot, echo=FALSE, warning = FALSE}
# calculate simple slopes
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(SlowWave.correct[!(is.na(SlowWave.correct$TrialCondition)),], aes(Trial, MeanCurr, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "FSW Amplitude (uV)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.06,.06,.06,.06)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(-5.5, 2)) +
#  ggtitle("Plotted with estimates from MLM") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

ggsave("./Figures/Figure3.tiff", width = 7, height = 5)

```
  
##### Simple slopes  
  
Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).   

``` {r simple, echo = FALSE}
# rescale trial
SlowWave.correct$Trial.begin = (SlowWave.correct$Trial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
SlowWave.correct$Trial.middle = SlowWave.correct$Trial.begin - 4
SlowWave.correct$Trial.end = SlowWave.correct$Trial.begin - 8

# calculate simple slopes
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("dark blue", "dark red", "light blue", "light red")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
fin
```  

#### Beginning of experiment 
The intercept and slopes of current and previous trial condition are allowed to vary by subject. The intercept is allowed to vary by electrode nested within subject.   
  
Trial is scaled to range from 0 to 8.  

Categorical variables are effect coded.  

``` {r model1, echo = FALSE}

m1 = lmer(MeanCurr ~ Current*Previous*Trial.begin + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = SlowWave.correct)
```

**Random effects:**  
``` {r model1random, echo = FALSE}
summary(m1)$varcor
```

**Fixed effects:**
``` {r model1fixed, echo = FALSE} 
round(summary(m1)$coefficients[c(1:3,5),1:5], digits = 3)
round(summary(m1)$coefficients[c(4,6:8),1:5], digits = 3)
```

**Marginal means:**  
Error bars represent standard error.  
``` {r model1marginal, echo = FALSE}
# use dummy coded model
# was calculated earlier for simple slopes (fm2)
parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plotting
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)

condColors = c("forestgreen", "Black")
condLinetype = c("dashed", "solid")

ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("Beginning") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

  
```


#### Middle of experiment 
Trial is shifted so that trial ranges from -4 to 4.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*  

**Fixed effects:**
``` {r model2, echo = FALSE}
# effect
m2 = lmer(MeanCurr ~ Current*Previous*Trial.middle + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

round(summary(m2)$coefficients[c(1:3,5),1:5], digits = 3)

```
**Marginal means:**  
Error bars represent standard error.  
``` {r model2marginal, echo = FALSE}
# use dummy coded model
fm3 <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = SlowWave.correct)
parms <- fixef(fm3) # fixed parameters from model
vcmat <- vcov(fm3) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("Middle") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```


#### End of experiment 
Trial is shifted so that trial ranges from -8 to 0.  
*Just the fixed effects of Current and Previous are shown, the random effects and fixed effects of any Trial interactions will be the same as the first model.*
  
**Fixed effects:**
``` {r model3, echo = FALSE}
m3 = lmer(MeanCurr ~ Current*Previous*Trial.end + 
       (Current*Previous|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

round(summary(m3)$coefficients[c(1:3,5),1:5], digits = 3)

```

**Marginal means:**  
Error bars represent standard error.  
``` {r model3marginal, echo = FALSE}
# use dummy coded model
fm4 <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + # need to use dummy coded variables, not effect coded
              (Condition*prevCond|Subject) + (1|Electrode:Subject), data = SlowWave.correct)
parms <- fixef(fm4) # fixed parameters from model
vcmat <- vcov(fm4) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plotting
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=condColors, guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=condLinetype, guide = F) +
  xlab("Previous Trial") +
  theme_bw() +
  ggtitle("End") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size=20),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16))

```

