---
title: Disaggregate analyses
author: Hannah, 6/29/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(dplyr)
require(lme4)
require(lmerTest)
require(ggplot2)
require(knitr)
#setwd("C:/Users/Curt/Box Sync/Bruce Projects/Sequential Processing/PointByPoint Processing/Created by R_ArtRej")
MeanCent_dat = read.delim("RT_N1_N2_FSW_FSWPrev_MeanCent.txt")
MeanCent_dat$RT[MeanCent_dat$RT == -7] = NA

MeanCent_dat$Trial.scaled = (MeanCent_dat$Trial-1)/100

MeanCent_dat = filter(MeanCent_dat, !(Subject == 4 & (Trial >= 401 & Trial <=600)))
```
**Major changes: Reknitted with new data (trials fixed for subs 2, 4, 8, 16, 17, 19, 30, 59, 70, 72). Doesn't include 19, 74, or 137 because of difficulty matching up RT and ERP data. Block 3 of Subject 4 is also excluded.**

**Includes FSW -> N1.**

**Sample includes 33 subjects.**  

The subject mean and subject mean centered variables have been computed for SlowWavePrev.

A datapoint will be included if:  

1) Current trial is not rejected due to artifacts.  
2) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
3) Both current trial and previous trial are correct.
4) Previous trial has not been rejecred due to artifacts.

SlowWaveMean indicates the between-subject effect.  
SlowWaveCent indicates the within-subject effect.  

### 1. SW on one trial predicting N2 on the following trial
```{r data1}
Dis_N2_Out = lmer(N2Curr ~ SWPrevMean + SWPrevCent +
                    (1|Subject), data = MeanCent_dat)
```

**Random effects:**  
``` {r grand1random, echo = FALSE}
summary(Dis_N2_Out)$varcor
```

**Fixed effects:**
``` {r grand1fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_N2_Out)$coefficients, digits = 3))
kable(est)
```



#### A. SW on one trial predicting N2 on the following trial, including trial as a predictor
```{r Adata1}
Dis_N2_Out = lmer(N2Curr ~ SWPrevMean + SWPrevCent*Trial.scaled +
                    (1|Subject), data = MeanCent_dat)
```

**Random effects:**  
``` {r Agrand1random, echo = FALSE}
summary(Dis_N2_Out)$varcor
```

**Fixed effects:**
``` {r Agrand1fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_N2_Out)$coefficients, digits = 3))
kable(est)
```

#### A2. SW on one trial predicting N2 on the following trial, within particular conditions
```{r Adata1.2, echo = F}
MeanCent_dat$Current[MeanCent_dat$Cell == "Previous incompatible - Current compatible"] = "Compatible"
MeanCent_dat$Current[MeanCent_dat$Cell == "Previous incompatible - Current incompatible"] = "Incompatible"
MeanCent_dat$Current[MeanCent_dat$Cell == "Previous compatible - Current compatible"] = "Compatible"
MeanCent_dat$Current[MeanCent_dat$Cell == "Previous compatible - Current incompatible"] = "Incompatible"

MeanCent_dat$Previous[MeanCent_dat$Cell == "Previous incompatible - Current compatible"] = "Incompatible"
MeanCent_dat$Previous[MeanCent_dat$Cell == "Previous incompatible - Current incompatible"] = "Incompatible"
MeanCent_dat$Previous[MeanCent_dat$Cell == "Previous compatible - Current compatible"] = "Compatible"
MeanCent_dat$Previous[MeanCent_dat$Cell == "Previous compatible - Current incompatible"] = "Compatible"

```

Including Current and Previous as predictors:  
**Random effects:**  
``` {r }
m1 = lmer(N2Curr ~ SWPrevMean + SWPrevCent*CondCurr*CondPrev +
                    (1|Subject), data = MeanCent_dat)

summary(m1)$varcor
```

**Fixed effects:**
``` {r } 
est = as.data.frame(round(summary(m1)$coefficients, digits = 3))
kable(est)
```

Same thing, but separately for each type of trial:  
**iI**  
``` {r PICI, echo = FALSE}
PICI = lmer(N2Curr ~ SWPrevMean + SWPrevCent +
                    (1|Subject), data = filter(MeanCent_dat, Cell == "Previous incompatible - Current incompatible"))

kable(round(summary(PICI)$coefficients, digits = 3))
```

**cI**  
``` {r PCCI, echo = FALSE}
PCCI = lmer(N2Curr ~ SWPrevMean + SWPrevCent +
                    (1|Subject), data = filter(MeanCent_dat, Cell == "Previous compatible - Current incompatible"))

kable(round(summary(PCCI)$coefficients, digits = 3))
```

**iC**  
``` {r iC, echo = FALSE}
iC = lmer(N2Curr ~ SWPrevMean + SWPrevCent +
                    (1|Subject), data = filter(MeanCent_dat, Cell == "Previous incompatible - Current compatible"))

kable(round(summary(iC)$coefficients, digits = 3))
```

**cC**  
``` {r cC, echo = FALSE}
cC = lmer(N2Curr ~ SWPrevMean + SWPrevCent +
                    (1|Subject), data = filter(MeanCent_dat, Cell == "Previous compatible - Current compatible"))

kable(round(summary(cC)$coefficients, digits = 3))
```


### 2. SlowWave on one trial predicting RT on the following trial
```{r data2}
Dis_RT_Out = lmer(RT ~ SWPrevMean + SWPrevCent + 
                    (1|Subject), data = MeanCent_dat)
```
  
**Random effects:**  
``` {r grand2random, echo = FALSE}
summary(Dis_RT_Out)$varcor
```

**Fixed effects:**
``` {r grand2fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_RT_Out)$coefficients, digits = 3))
kable(est)
```



#### B. SW on one trial predicting RT on the following trial, including trial as a predictor
```{r Bdata1}
Dis_N2_Out = lmer(RT ~ SWPrevMean + SWPrevCent*Trial.scaled +
                    (1|Subject), data = MeanCent_dat)
```

**Random effects:**  
``` {r Bgrand1random, echo = FALSE}
summary(Dis_N2_Out)$varcor
```

**Beginning of experiment:**
``` {r Bgrand1fixed, echo = FALSE} 
est1 = as.data.frame(round(summary(Dis_N2_Out)$coefficients, digits = 3))
kable(est1)
```

### 3. N2 on one trial predicting FSW on the same trial

```{r data5}
# need to add mean centered N2 and N2 sub means
submeans = select(MeanCent_dat, Subject, N2Curr) %>% 
  group_by(Subject) %>% 
  summarise_each(funs(mean(., na.rm=T))) %>% 
  as.data.frame()

MeanCent_dat$N2CurrMean = NA
for (i in unique(MeanCent_dat$Subject)) {
  MeanCent_dat$N2CurrMean[MeanCent_dat$Subject == i] = submeans$N2Curr[submeans$Subject == i]
}

MeanCent_dat$N2CurrCent = MeanCent_dat$N2Curr - MeanCent_dat$N2CurrMean

Dis_SW_Out = lmer(SlowWaveCurr ~ N2CurrMean + N2CurrCent + 
                    (1|Subject), data = MeanCent_dat)
```
  
**Random effects:**  
``` {r grand5random, echo = FALSE}
summary(Dis_SW_Out)$varcor
```

**Fixed effects:**
``` {r grand5fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_SW_Out)$coefficients, digits = 3))
kable(est)
```


#### E. N2 on one trial predicting FSW on the same trial, including trial as a predictor
```{r Ddata5}
Dis_SW_Out2 = lmer(SlowWaveCurr ~ N2CurrMean + N2CurrCent*Trial.scaled + 
                    (1|Subject), data = MeanCent_dat)
```

**Random effects:**  
``` {r Dgrand5random, echo = FALSE}
summary(Dis_SW_Out2)$varcor
```

**Fixed effects:**
``` {r Dgrand5fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_SW_Out2)$coefficients, digits = 3))
kable(est)
```

### 4. SlowWave on one trial predicting N1 on the following trial
```{r data4}
Dis_N1_Out = lmer(N1Curr ~ SWPrevMean + SWPrevCent + 
                    (1|Subject), data = MeanCent_dat)
```
  
**Random effects:**  
``` {r grand4random, echo = FALSE}
summary(Dis_N1_Out)$varcor
```

**Fixed effects:**
``` {r grand4fixed, echo = FALSE} 
est = as.data.frame(round(summary(Dis_N1_Out)$coefficients, digits = 3))
kable(est)
```



#### B. SW on one trial predicting N1 on the following trial, including trial as a predictor
```{r Bdata4}
Dis_N1_Out = lmer(N1Curr ~ SWPrevMean + SWPrevCent*Trial.scaled +
                    (1|Subject), data = MeanCent_dat)
```

**Random effects:**  
``` {r Bgrand4random, echo = FALSE}
summary(Dis_N1_Out)$varcor
```

**Beginning of experiment:**
``` {r Bgrand4fixed, echo = FALSE} 
est1 = as.data.frame(round(summary(Dis_N1_Out)$coefficients, digits = 3))
kable(est1)
```

