---
title: Repetition analyses (RT)
author: Hannah, 6/19/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = '50%')
options(width=140)
require(dplyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
```

### 1. REACTION TIME
Uses RT data from Alc Caf for condition 4 (Placebo-placebo) and condition 5 (Control).

“Current” trial will be included if:  
1) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
2) Both current trial and previous trial are correct.  
3) RT is longer than 200 ms and shorter than 2000 ms.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  

Each subject did 800 trials, with 100 trials in each of 8 blocks.

**Total sample is 50 subjects.**

Trigger Codes:
Comp: Target Left, Flanker Left = 110.  
Comp: Target Right, Flanker Right = 130.  
Incomp: Target Left, Flanker Right = 150.  
Incomp: Target Right, Flanker Left = 170.  

CompleteRep (24.3%) = repetition of same trial (e.g., excludes 110 following 110)    
AnyRep (74.8%) = either target or flanker is repeated (only includes 110/130 pair, 150/170 pair)  
TargetRep (25.3%) = target is repeated (excludes 150/110 pair, 170/130 pair)  
FlankerRep (25.2%) = flanker is repeated (excludes 150/130 pair, 170/110 pair)  

```{r RTdata, echo = FALSE}
dat = read.delim("RT_AllSubs_TBT_Cond_Prev_Rep.txt")
dat = dat[dat$ACC == 1 & dat$PrevTrialACC == 1,]

# discard trials for which RT is less than 100 and greater than 2000
dat$RTdrop = dat$RT_Raw
dat$RTdrop[dat$RT_Raw < 100] = NA
dat$RTdrop[dat$RT_Raw > 2000] = NA

# add trial information
dat$prevTrialType = NA
dat$prevTrialType[dat$PrevTrialType == 1] = "compatible"
dat$prevTrialType[dat$PrevTrialType == 2] = "incompatible"
dat$prevTrialType = factor(dat$prevTrialType)

# select subjects in Condition 4 and 5, take out 92 and 64
dat.use = dat[dat$Condition == 4|dat$Condition == 5,] %>% 
  filter(Subject != 92) %>% 
  filter(Subject != 64)

dat.use$Condition = paste(dat.use$prevTrialType, dat.use$TrialType, sep="_")

tapply(dat.use$RTdrop100_2000, dat.use$TrialType, mean)
tapply(dat.use$RTdrop100_2000, dat.use$Condition, mean)

# make effect coding variables
dat.use$Current.e = NA
dat.use$Current.e[dat.use$TrialType == "compatible"] = -1
dat.use$Current.e[dat.use$TrialType == "Incompatible"] = 1

dat.use$Previous.e = NA
dat.use$Previous.e[dat.use$prevTrialType == "compatible"] = -1
dat.use$Previous.e[dat.use$prevTrialType == "incompatible"] = 1

# add label for trial condition
dat.use$TrialCondition = "Previous compatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "compatible" & dat.use$TrialType == "compatible"] = 
  "Previous compatible - Current compatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "Incompatible"] = 
  "Previous incompatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "compatible"] = 
  "Previous incompatible - Current compatible"
dat.use$TrialCondition = factor(dat.use$TrialCondition)

# data set up in 8 blocks, trial goes 1-100 in each block
# add column for trial number across whole experiment so it goes 1-800
dat.use$ExpTrial = dat.use$Trial + (100*(dat.use$Block - 1))

# rescale trial
dat.use$Trial.begin = (dat.use$ExpTrial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
dat.use$Trial.middle = dat.use$Trial.begin - 4
dat.use$Trial.end = dat.use$Trial.begin - 8


```
#### A. TargetRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r trialLevel, echo = FALSE, warning = FALSE}

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
plot1.d <- lmer(RTdrop ~ TrialType*prevTrialType*ExpTrial + (TrialType+prevTrialType|Subject), data = filter(dat.use, TargetRep == 0))

parms <- fixef(plot1.d) # fixed parameters from model
vcmat <- vcov(plot1.d) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(filter(dat.use, TargetRep == 0), aes(ExpTrial, RTdrop, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "Reaction Time (ms)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(325, 500))
#  ggtitle("Plotted with estimates from MLM") +  
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r simple, echo = FALSE}

# find slopes with dummy coded model, trial is scaled
begin.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.begin + (TrialType+prevTrialType|Subject), data = filter(dat.use, TargetRep == 0))

parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("blue dashed", "red dashed", "blue solid", "red solid")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.begin + (Current.e*Previous.e|Subject), data = filter(dat.use, TargetRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
begin.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.begin + (TrialType+prevTrialType|Subject), data = filter(dat.use, TargetRep == 0))
parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.middle + (Current.e*Previous.e|Subject), data = filter(dat.use, TargetRep == 0))

kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.middle + (TrialType+prevTrialType|Subject), data = filter(dat.use, TargetRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.end + (Current.e*Previous.e|Subject), data = filter(dat.use, TargetRep == 0))

kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.end + (TrialType+prevTrialType|Subject), data = filter(dat.use, TargetRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

#### B. CompleteRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r trialLevel2, echo = FALSE, warning = FALSE}

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
plot1.d <- lmer(RTdrop ~ TrialType*prevTrialType*ExpTrial + (TrialType+prevTrialType|Subject), data = filter(dat.use, CompleteRep == 0))

parms <- fixef(plot1.d) # fixed parameters from model
vcmat <- vcov(plot1.d) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(filter(dat.use, CompleteRep == 0), aes(ExpTrial, RTdrop, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "Reaction Time (ms)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(325, 500))
#  ggtitle("Plotted with estimates from MLM") +  
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r}

# find slopes with dummy coded model, trial is scaled
begin.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.begin + (TrialType+prevTrialType|Subject), data = filter(dat.use, CompleteRep == 0))

parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("blue dashed", "red dashed", "blue solid", "red solid")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.begin + (Current.e*Previous.e|Subject), data = filter(dat.use, CompleteRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
begin.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.begin + (TrialType+prevTrialType|Subject), data = filter(dat.use, CompleteRep == 0))
parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.middle + (Current.e*Previous.e|Subject), data = filter(dat.use, CompleteRep == 0))

kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.middle + (TrialType+prevTrialType|Subject), data = filter(dat.use, CompleteRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(RTdrop ~ Current.e*Previous.e*Trial.end + (Current.e*Previous.e|Subject), data = filter(dat.use, CompleteRep == 0))

kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(RTdrop ~ TrialType*prevTrialType*Trial.end + (TrialType+prevTrialType|Subject), data = filter(dat.use, CompleteRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("Reaction Time (ms)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(350, 475)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```
