---
title: Repetition analyses (N2)
author: Hannah, 6/19/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(out.width = '50%')
options(width=140)
require(dplyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
```

### 1. N2
“Current” trial will be included if:  
1) Current trial is not rejected due to artifacts.  
2) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
3) Both current trial and previous trial are correct.  

The following electrodes are included: F3, Fz, F4, FC3, FCz, FC4, C3, Cz, C4.

The following subjects were excluded:
- 92 (wrong number of trials, possibly data collection error)
- 64 (<50% accuracy rate)
- 65 (only 187 usable trials (23.3%))

One or more electrodes were bad for subjects 19, 74, and 137 (data from those electrodes is discarded).

Besides that, ERP data is completely missing for subs 36, 37, 39, 40, 42, 43, 46, 51, 53, 54, 56, 57, 78.

**Total sample is 36 subjects.**

Trigger Codes:
Comp: Target Left, Flanker Left = 110.  
Comp: Target Right, Flanker Right = 130.  
Incomp: Target Left, Flanker Right = 150.  
Incomp: Target Right, Flanker Left = 170.  

CompleteRep (24.3%) = repetition of same trial (e.g., excludes 110 following 110)    
AnyRep (74.8%) = either target or flanker is repeated (only includes 110/130 pair, 150/170 pair)  
TargetRep (25.3%) = target is repeated (excludes 150/110 pair, 170/130 pair)  
FlankerRep (25.2%) = flanker is repeated (excludes 150/130 pair, 170/110 pair)  

```{r}
N2.correct = read.delim("./N2_AllSubs_TBT_Cond_Prev_Rep.txt") # made by Curt. Same number of trials as "AllSubs_TBTaverages_N2_Correct_withPrevious_EventFixed.txt", which was used in submission 1 analyses

# add effect codes for categorical variables
N2.correct$Previous = NA
N2.correct$Previous[N2.correct$prevCond == "compat"] = -1
N2.correct$Previous[N2.correct$prevCond == "incompat"] = 1

N2.correct$Current = NA
N2.correct$Current[N2.correct$Condition == "Comp"] = -1
N2.correct$Current[N2.correct$Condition == "InComp"] = 1

# rescale trial
N2.correct$Trial.begin = (N2.correct$Trial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
N2.correct$Trial.middle = N2.correct$Trial.begin - 4
N2.correct$Trial.end = N2.correct$Trial.begin - 8

```
#### A. TargetRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r}

# calculate simple slopes
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, TargetRep == 0))

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc))

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc))

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(N2.correct[!(is.na(N2.correct$TrialCondition)),], aes(Trial, MeanCurr, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "N2 Amplitude (uV)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.06,.06,.06,.06)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(-2.5, 5)) 
#  ggtitle("Plotted with estimates from MLM") +
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r simpleN2, echo = FALSE}

fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, TargetRep == 0))

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc))

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("dashed blue", "dashed red", "solid blue", "solid red")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(MeanCurr ~ Current*Previous*Trial.begin + (Current*Previous|Subject), data = filter(N2.correct, TargetRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
parms <- fixef(fm2) # fixed parameters from model (run earlier in simple slopes)
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(MeanCurr ~ Current*Previous*Trial.middle + (Current*Previous|Subject), data = filter(N2.correct, TargetRep == 0))

kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, TargetRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(MeanCurr ~ Current*Previous*Trial.end + (Current*Previous|Subject), data = filter(N2.correct, TargetRep == 0))


kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, TargetRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

#### B. CompleteRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r}

# calculate simple slopes
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, CompleteRep == 0))

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc))

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc))

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(N2.correct[!(is.na(N2.correct$TrialCondition)),], aes(Trial, MeanCurr, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "N2 Amplitude (uV)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.06,.06,.06,.06)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(-2.5, 5)) 
#  ggtitle("Plotted with estimates from MLM") +
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r simpleN2, echo = FALSE}

fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, CompleteRep == 0))

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc))

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("dashed blue", "dashed red", "solid blue", "solid red")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(MeanCurr ~ Current*Previous*Trial.begin + (Current*Previous|Subject), data = filter(N2.correct, CompleteRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
parms <- fixef(fm2) # fixed parameters from model (run earlier in simple slopes)
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(MeanCurr ~ Current*Previous*Trial.middle + (Current*Previous|Subject), data = filter(N2.correct, CompleteRep == 0))

kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, CompleteRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(MeanCurr ~ Current*Previous*Trial.end + (Current*Previous|Subject), data = filter(N2.correct, CompleteRep == 0))


kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(N2.correct, CompleteRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("N2 amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(.2, 4.2)) +
  scale_color_manual(values=c("black", "forestgreen"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

