---
title: Repetition analyses (FSW)
author: Hannah, 6/30/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = '50%')
knitr::opts_chunk$set(warning = FALSE)
options(width=140)
require(dplyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
```
**Major changes: Fixed FlankerRep and TargetRep to include duplications (e.g., 130 followed by 130). Added model with TargetRep included as covariate.**


### 1. FSW
“Current” trial will be included if:  
1) Current trial is not rejected due to artifacts.  
2) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
3) Both current trial and previous trial are correct.  

The following electrodes are included: F3, Fz, F4, FC3, FCz, FC4, C3, Cz, C4.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  
- 65 (only 187 usable trials (23.3%))

One or more electrodes were bad for subjects 19, 74, and 137 (data from those electrodes is discarded).  

Besides that, ERP data is completely missing for subs 36, 37, 39, 40, 42, 43, 46, 51, 53, 54, 56, 57, 78.
  
**Total sample is 36 subjects.**  

Trigger Codes:
Comp: Target Left, Flanker Left = 110.  
Comp: Target Right, Flanker Right = 130.  
Incomp: Target Left, Flanker Right = 150.  
Incomp: Target Right, Flanker Left = 170.  

CompleteRep (24.3%) = repetition of same trial (e.g., excludes 110 following 110)    
AnyRep (74.8%) = either target or flanker is repeated (only includes 110/130 pair, 150/170 pair)  
TargetRep (~50%) = target is repeated (excludes 150/110 pair, 170/130 pair)  
FlankerRep (~50%) = flanker is repeated (excludes 150/130 pair, 170/110 pair)  

```{r}
SlowWave.correct = read.delim("FSW_AllSubs_TBT_Cond_Prev_Rep.txt")

# Fix TargetRep and FlankerRep columns to flag duplications
SlowWave.correct$TargetRep[SlowWave.correct$prevCondTrigger == SlowWave.correct$currCondTrigger] = 1
SlowWave.correct$FlankerRep[SlowWave.correct$prevCondTrigger == SlowWave.correct$currCondTrigger] = 1

# make effect coding variables
SlowWave.correct$Current.e = NA
SlowWave.correct$Current.e[SlowWave.correct$Condition == "Comp"] = -1
SlowWave.correct$Current.e[SlowWave.correct$Condition == "InComp"] = 1

SlowWave.correct$Previous.e = NA
SlowWave.correct$Previous.e[SlowWave.correct$prevCond == "compat"] = -1
SlowWave.correct$Previous.e[SlowWave.correct$prevCond == "incompat"] = 1

# rescale trial
SlowWave.correct$Trial.begin = (SlowWave.correct$Trial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
SlowWave.correct$Trial.middle = SlowWave.correct$Trial.begin - 4
SlowWave.correct$Trial.end = SlowWave.correct$Trial.begin - 8


```
#### A. TargetRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r trialLevel, echo = FALSE, warning = FALSE}

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
fm2 <- lmer(MeanCurr ~ Condition*prevCond*Trial + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))

parms <- fixef(fm2) # fixed parameters from model
vcmat <- vcov(fm2) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(filter(SlowWave.correct, TargetRep == 0), aes(Trial, MeanCurr, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "FSW amplitude (uV)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(-5.5, 2))
#  ggtitle("Plotted with estimates from MLM") +  
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r simple, echo = FALSE}

# find slopes with dummy coded model, trial is scaled
begin.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))

parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("blue dashed", "red dashed", "blue solid", "red solid")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.begin + 
       (Current.e*Previous.e|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.middle + 
       (Current.e*Previous.e|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))
kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.end + 
       (Current.e*Previous.e|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))
kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + # need to use dummy coded variables, not effect coded
       (Condition*prevCond|Subject) + (1|Electrode:Subject), data = filter(SlowWave.correct, TargetRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no TargetRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

#### B. CompleteRep trials taken out

##### Plot over whole task 
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r trialLevel2, echo = FALSE, warning = FALSE}

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
plot1.d <- lmer(MeanCurr ~ Condition*prevCond*Trial + (Condition+prevCond|Subject), data = filter(SlowWave.correct, CompleteRep == 0))

parms <- fixef(plot1.d) # fixed parameters from model
vcmat <- vcov(plot1.d) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,4,8)
STmat[1,] <- c(rep(0,3),1,0,0,0,0) # slope for current = 0, previous = 0 (current compat-previous compat)
STmat[2,] <- c(rep(0,3),1,0,0,1,0) # slope for current = 0, previous = 1 (current compat-previous incompat)
STmat[3,] <- c(rep(0,3),1,0,1,0,0) # slope for current = 1, previous = 0 (current incompat-previous compat)
STmat[4,] <- c(rep(0,3),1,0,1,1,1) # slope for current = 1, previous = 1 (current incompat-previous incompat)

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,4,8)
ITmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
ITmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
ITmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
ITmat[4,] <- c(1,1,1,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = c("Previous compatible - Current compatible",
                          "Previous incompatible - Current compatible",
                          "Previous compatible - Current incompatible",
                          "Previous incompatible - Current incompatible")


# BINGO -------------------------------------------------------------------
ggplot(filter(SlowWave.correct, CompleteRep == 0), aes(Trial, MeanCurr, alpha = TrialCondition, color = TrialCondition, shape = TrialCondition)) +
  geom_point() +
  geom_abline(data = forPlotting, aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "FSW amplitude (uV)") +
  scale_shape_manual(values=c(1,19,1,19)) +
  scale_alpha_manual(values=c(.1,.1,.1,.1)) +
  scale_color_manual(values=c("blue", "blue", "red", "red")) +
  scale_linetype_manual(values=c("longdash", "solid", "longdash", "solid")) +
  theme_bw() +
  coord_cartesian(ylim=c(-5.5, 2))
#  ggtitle("Plotted with estimates from MLM") +  
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))
```

##### Simple slopes

Trial is scaled to range from 0 to 8 (instead of 1 to 800) so that the betas associated with trial are a little bigger (but significance testing is unaffected by linear scaling, so the test statistics and p values will be the same as if we used the unscaled Trial variable).

``` {r}

# find slopes with dummy coded model, trial is scaled
begin.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + (Condition+prevCond|Subject), data = filter(SlowWave.correct, CompleteRep == 0))

parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(rep(0,3),1,0,0,0,0) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(rep(0,3),1,0,0,1,0) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(rep(0,3),1,0,1,0,0) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(rep(0,3),1,0,1,1,1) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## final results
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE

fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

fin = format(fin, digits = 3)

# relabel for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Color = c("blue dashed", "red dashed", "blue solid", "red solid")

fin = rename(fin, Estimate = est, SE = ses, ci95_lower = lbnd, ci95_upper = ubnd)

# display
kable(fin)
```

##### Fixed effects of Trial and interactions with Trial:  
Trial is centered and scaled to range from -4 to 4.

``` {r}
begin.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.begin + (Current.e*Previous.e|Subject), data = filter(SlowWave.correct, CompleteRep == 0))

kable(round(summary(begin.e)$coefficients[c(4, 6:8),1:5], digits = 3))
```

##### Fixed effects at beginning of task:  
```{r}
kable(round(summary(begin.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
begin.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.begin + (Condition+prevCond|Subject), data = filter(SlowWave.correct, CompleteRep == 0))
parms <- fixef(begin.d) # fixed parameters from model
vcmat <- vcov(begin.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Beginning (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at middle of task:  
```{r}
middle.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.middle + (Current.e*Previous.e|Subject), data = filter(SlowWave.correct, CompleteRep == 0))

kable(round(summary(middle.e)$coefficients[c(1:3,5),1:5], digits = 3))
```

**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
middle.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.middle + (Condition+prevCond|Subject), data = filter(SlowWave.correct, CompleteRep == 0))
parms <- fixef(middle.d) # fixed parameters from model
vcmat <- vcov(middle.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("Middle (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

##### Fixed effects at end of task:  
```{r}
end.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.end + (Current.e*Previous.e|Subject), data = filter(SlowWave.correct, CompleteRep == 0))

kable(round(summary(end.e)$coefficients[c(1:3,5),1:5], digits = 3))
```
    
**Marginal means:**  
Error bars represent standard error.  
``` {r}
# use dummy coded model
end.d <- lmer(MeanCurr ~ Condition*prevCond*Trial.end + (Condition+prevCond|Subject), data = filter(SlowWave.correct, CompleteRep == 0))
parms <- fixef(end.d) # fixed parameters from model
vcmat <- vcov(end.d) # variance/covariance matrix of fixed effects

## each row of this matrix defines entries of parms that we want to combine:
Tmat <- matrix(NA,4,8)
Tmat[1,] <- c(1,0,0,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 0 (current compat-previous compat)
Tmat[2,] <- c(1,0,1,0,0,rep(0,3)) # weights for estimates for current = 0, previous = 1 (current compat-previous incompat)
Tmat[3,] <- c(1,1,0,0,0,rep(0,3)) # weights for estimates for current = 1, previous = 0 (current incompat-previous compat)
Tmat[4,] <- c(1,1,0,0,1,rep(0,3)) # weights for estimates for current = 1, previous = 1 (current incompat-previous incompat)

parest <- Tmat %*% parms          # see above for notation
newvc <- Tmat %*% vcmat %*% t(Tmat)
ses <- sqrt(diag(newvc)) 

## calculate estimates, standard error
fin = cbind(parest, ses) %>% as.data.frame()
names(fin) = c("est", "ses")

# to calculate 95% CI intervals, lower bound = m - 2*SE, upper bound = m + 2*SE
fin$lbnd = fin$est - 2*fin$ses
fin$ubnd = fin$est + 2*fin$ses

# format for understanding
fin$Current = c("Compat", "Compat", "Incompat", "Incompat")
fin$Previous = c("Compat", "Incompat", "Compat", "Incompat")
fin$Previous = factor(fin$Previous)
fin$Current = factor(fin$Current)
fin = rename(fin, Estimate = est, SE = ses) 

# for plot
limits <- aes(ymax = Estimate + SE, ymin=Estimate - SE)
ggplot(fin, aes(x = Previous, y = Estimate, group = Current, color = Current, linetype = Current)) +
  geom_line() +
  geom_point(size = 4) +
  geom_errorbar(limits, width=0.2, linetype="solid") +
  ylab("FSW amplitude (uV)") +
  xlab("Previous Trial") +
  coord_cartesian(ylim = c(-4.2, -.2)) +
  scale_color_manual(values=c("black", "red"), guide = guide_legend(title = "Current trial")) +
  scale_linetype_manual(values=c("solid", "dashed"), guide = F) +
  theme_bw() +
  ggtitle("End (no CompleteRep)") 
  # theme(plot.title = element_text(hjust = 0.5, size = 20),
  #       axis.title = element_text(size=20),
  #       axis.text.x = element_text(size=16),
  #       axis.text.y = element_text(size=16))

```

#### C. TargetRep trials retained, included as covariate

##### Plot over whole task, separately for TargetRep and non-TargetRep  
**Slopes and estimates of lines are from the MLM, not fitted with OLS.** 

``` {r}

# find slopes and intercepts with dummy coded model, trial (unscaled) is included
plot1.d <- lmer(MeanCurr ~ Condition*prevCond*Trial*TargetRep + (1|Subject) + (1|Electrode:Subject), data = SlowWave.correct)

parms <- fixef(plot1.d) # fixed parameters from model
vcmat <- vcov(plot1.d) # variance/covariance matrix of fixed effects

# First calculate slopes

## each row of this matrix defines entries of parms that we want to combine:
STmat <- matrix(NA,8,16)
STmat[1,] <- c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0) # slope for cC, TargetRep = 0
STmat[2,] <- c(0,0,0,1,0,0,0,1,0,0,0,0,0,0,0,0) # slope for iC, TargetRep = 0
STmat[3,] <- c(0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0) # slope for cI, TargetRep = 0
STmat[4,] <- c(0,0,0,1,0,0,1,1,0,0,0,1,0,0,0,0) # slope for iI, TargetRep = 0

STmat[5,] <- c(0,0,0,1,0,0,0,0,0,0,1,0,0,0,0,0) # slope for cC, TargetRep = 1
STmat[6,] <- c(0,0,0,1,0,0,0,1,0,0,1,0,0,0,1,0) # slope for iC, TargetRep = 1
STmat[7,] <- c(0,0,0,1,0,0,1,0,0,0,1,0,0,1,0,0) # slope for cI, TargetRep = 1
STmat[8,] <- c(0,0,0,1,0,0,1,1,0,0,1,1,0,1,1,1) # slope for iI, TargetRep = 1

Sparest <- STmat %*% parms          # see above for notation
Snewvc <- STmat %*% vcmat %*% t(STmat)
Sses <- sqrt(diag(Snewvc)) 

slopes = cbind(Sparest, Sses) %>% as.data.frame()
names(slopes) = c("Slope", "Slope_SE")

# Next calculate intercepts

## each row of this matrix defines entries of parms that we want to combine:
ITmat <- matrix(NA,8,16)
ITmat[1,] <- c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0) # intercept for cC, TargetRep = 0
ITmat[2,] <- c(1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0) # intercept for iC, TargetRep = 0
ITmat[3,] <- c(1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0) # intercept for cI, TargetRep = 0
ITmat[4,] <- c(1,1,1,0,0,1,0,0,0,0,0,0,0,0,0,0) # intercept for iI, TargetRep = 0

ITmat[5,] <- c(1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0) # intercept for cC, TargetRep = 1
ITmat[6,] <- c(1,0,1,0,1,0,0,0,0,1,0,0,0,0,0,0) # intercept for iC, TargetRep = 1
ITmat[7,] <- c(1,1,0,0,1,0,0,0,1,0,0,0,0,0,0,0) # intercept for cI, TargetRep = 1
ITmat[8,] <- c(1,1,1,0,1,1,0,0,1,1,0,0,1,0,0,0) # intercept for iI, TargetRep = 1

Iparest <- ITmat %*% parms          # see above for notation
Inewvc <- ITmat %*% vcmat %*% t(ITmat)
Ises <- sqrt(diag(Inewvc)) 

## final results
intercepts = cbind(Iparest, Ises) %>% as.data.frame()
names(intercepts) = c("Intercept", "Intercept_SE")

forPlotting = cbind(slopes, intercepts)

# label for understanding
forPlotting$TrialCondition = rep(c("cC", "iC", "cI", "iI"),2)
forPlotting$TrialCondition = factor(forPlotting$TrialCondition)
forPlotting$TargetRep = rep(c(0, 1), each=4)
forPlotting$TargetRep = factor(forPlotting$TargetRep)


# BINGO -------------------------------------------------------------------
ggplot(filter(SlowWave.correct, TargetRep == 0), aes(Trial, MeanCurr)) +
  geom_point(alpha=0) +
  geom_abline(data = forPlotting[1:4,], aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "FSW amplitude (uV)") +
  theme_bw() +
  ggtitle("No TargetRep (TargetRep = 0)") +
  coord_cartesian(ylim=c(-5.5, 2)) +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(filter(SlowWave.correct, TargetRep == 1), aes(Trial, MeanCurr)) +
  geom_point(alpha=0) +
  geom_abline(data = forPlotting[5:8,], aes(intercept=Intercept, slope=Slope, color = TrialCondition, linetype = TrialCondition), size=1)+
  labs(x = "Trial", y = "FSW amplitude (uV)") +
  theme_bw() +
  ggtitle("TargetRep (TargetRep = 1)") +
  coord_cartesian(ylim=c(-5.5, 2)) +
  theme(plot.title = element_text(hjust = 0.5))

```

##### Beginning of the task
Current and Previous are effect coded, trial ranges from 0 to 8.
``` {r}
begin.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.begin*TargetRep + (1|Subject), data = SlowWave.correct)

kable(round(summary(begin.e)$coefficients[c(1:3,6),1:5], digits = 3))
# interactions with trial
kable(round(summary(begin.e)$coefficients[c(4, 7:8, 12, 11, 14:16),1:5], digits = 3))
# interactions with target
kable(round(summary(begin.e)$coefficients[c(5, 9:10, 13),1:5], digits = 3))

```

##### Middle of the task
Current and Previous are effect coded, trial ranges from -4 to 4.
``` {r}
middle.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.middle*TargetRep + (1|Subject), data = SlowWave.correct)

kable(round(summary(middle.e)$coefficients[c(1:3,6),1:5], digits = 3))
kable(round(summary(middle.e)$coefficients[c(5, 9:10, 13),1:5], digits = 3))
```

##### End of the task
Current and Previous are effect coded, trial ranges from -8 to 0.
``` {r}
end.e = lmer(MeanCurr ~ Current.e*Previous.e*Trial.end*TargetRep + (1|Subject), data = SlowWave.correct)

kable(round(summary(end.e)$coefficients[c(1:3,6),1:5], digits = 3))
kable(round(summary(end.e)$coefficients[c(5, 9:10, 13),1:5], digits = 3))
```

