---
title: Target and Flanker Repetitions as a function of Trial, Current, and Previous. For RT only. Curt
author: CvonSleazy, 7/07/2017
output:
  html_document:
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = '50%')
knitr::opts_chunk$set(warning = FALSE)
options(width=140)
require(dplyr)
require(ggplot2)
require(lme4)
require(lmerTest)
require(knitr)
```
# REACTION TIME
Uses RT data from Alc Caf for condition 4 (Placebo-placebo) and condition 5 (Control).

A current trial will be included if:  
1) Current trial is not the first trial of the block (i.e. trial 1, 101, 201, 301 etc. are not included).  
2) Both current trial and previous trial are correct.  
3) RT is longer than 200 ms and shorter than 2000 ms.

The following subjects were excluded:  
- 92 (wrong number of trials, possibly data collection error)  
- 64 (<50% accuracy rate)  

Each subject did 800 trials, with 100 trials in each of 8 blocks.

**Total sample is 50 subjects.**

Trigger Codes:
Comp: Target Left, Flanker Left = 110.  
Comp: Target Right, Flanker Right = 130.  
Incomp: Target Left, Flanker Right = 150.  
Incomp: Target Right, Flanker Left = 170.  

CompleteRep (24.3%) = repetition of same trial (e.g., excludes 110 following 110)    
AnyRep (74.8%) = either target or flanker is repeated (only includes 110/130 pair, 150/170 pair)  
TargetRep (~50%) = target is repeated (excludes 150/110 pair, 170/130 pair)  
FlankerRep (~50%) = flanker is repeated (excludes 150/130 pair, 170/110 pair)  

```{r RTdata, echo = FALSE}
setwd("C:/Users/Curt/Box Sync/Bruce Projects/Sequential Processing/PointByPoint Processing/Manuscript/Review & Resubmission/Data")
dat = read.delim("RT_AllSubs_TBT_Cond_Prev_Rep.txt")
dat = dat[dat$ACC == 1 & dat$PrevTrialACC == 1,]
# discard trials for which RT is less than 100 and greater than 2000
dat$RTdrop = dat$RT_Raw
dat$RTdrop[dat$RT_Raw < 100] = NA
dat$RTdrop[dat$RT_Raw > 2000] = NA

# add trial information
dat$prevTrialType = NA
dat$prevTrialType[dat$PrevTrialType == 1] = "compatible"
dat$prevTrialType[dat$PrevTrialType == 2] = "incompatible"
dat$prevTrialType = factor(dat$prevTrialType)

# Fix TargetRep and FlankerRep columns to flag duplications
dat$TargetRep[dat$StimOnsetCode == dat$PrevStimOnsetCode] = 1
dat$FlankerRep[dat$StimOnsetCode == dat$PrevStimOnsetCode] = 1

# select subjects in Condition 4 and 5, take out 92 and 64
dat.use = dat[dat$Condition == 4|dat$Condition == 5,] %>% 
  filter(Subject != 92) %>% 
  filter(Subject != 64)

dat.use$Condition = paste(dat.use$prevTrialType, dat.use$TrialType, sep="_")

#tapply(dat.use$RTdrop100_2000, dat.use$TrialType, mean)
#tapply(dat.use$RTdrop100_2000, dat.use$Condition, mean)

# make effect coding variables
dat.use$Current.e = NA
dat.use$Current.e[dat.use$TrialType == "compatible"] = -1
dat.use$Current.e[dat.use$TrialType == "Incompatible"] = 1

dat.use$Previous.e = NA
dat.use$Previous.e[dat.use$prevTrialType == "compatible"] = -1
dat.use$Previous.e[dat.use$prevTrialType == "incompatible"] = 1

# add label for trial condition
dat.use$TrialCondition = "Previous compatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "compatible" & dat.use$TrialType == "compatible"] = 
  "Previous compatible - Current compatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "Incompatible"] = 
  "Previous incompatible - Current incompatible"
dat.use$TrialCondition[dat.use$prevTrialType == "incompatible" & dat.use$TrialType == "compatible"] = 
  "Previous incompatible - Current compatible"
dat.use$TrialCondition = factor(dat.use$TrialCondition)

# data set up in 8 blocks, trial goes 1-100 in each block
# add column for trial number across whole experiment so it goes 1-800
dat.use$ExpTrial = dat.use$Trial + (100*(dat.use$Block - 1))

# rescale trial
dat.use$Trial.begin = (dat.use$ExpTrial-2)/100
# shift trial to look at fixed effects at middle and end of task as well
dat.use$Trial.middle = dat.use$Trial.begin - 4
dat.use$Trial.end = dat.use$Trial.begin - 8

```
#Analyses
####I examine both Target Reps and Flanker Reps separetly, as a function of previous, current, and trial. It turns out that Complete Reps and Any Reps are confounded with trialtype. That is, Complete Reps are only possible for two of the possible four congruency-pair conditions, namely for cong-cong and incong-incong. Moreover, a lack of Any Rep is only possible on cong-incong and incong-cong pairs. This is my best guess as to why trying to run the models below with Complete Rep and Any Rep results in "rank deficiency".

##Target repetitions.
###Repetition by current by previous by trial.
``` {r}
TargetRep = lmer(RTdrop ~ Current.e * Previous.e * TargetRep * Trial.begin + (1|Subject), data = dat.use)
summary(TargetRep)
```
###Target Rep follow-up analyses.
###Testing the thee-way interaction.
``` {r}
TargetRep = lmer(RTdrop ~ Current.e * Previous.e * TargetRep + (1|Subject), data = dat.use)
summary(TargetRep)
```
###Removing trial since there was no four-way and breaking down the significant three-way between current, previous, and target rep.
###Without repetitions.
``` {r}
TargetRep_0 = lmer(RTdrop ~ Current.e * Previous.e + (1|Subject), data = filter(dat.use, TargetRep == 0))
summary(TargetRep_0)
```
###Only Repetitions
```{r}
TargetRep_1 = lmer(RTdrop ~ Current.e * Previous.e + (1|Subject), data = filter(dat.use, TargetRep == 1))
summary(TargetRep_1)
```
###Examining Current by Repetition effects.
``` {r}
TargetRep_0 = lmer(RTdrop ~ Current.e * TargetRep + (1|Subject), data = dat.use)
summary(TargetRep_0)
```


##Flanker repetitions.
```{r}
FlankerRep = lmer(RTdrop ~ Current.e * Previous.e * FlankerRep * Trial.begin + (1|Subject), data = dat.use)
summary(FlankerRep)
```
###Flanker Rep follow-up analyses.
###Breaking down four-way for flanker rep as a function of trial.
###Beginning
```{r}
FlankerRep_Begin = lmer(RTdrop ~ Current.e * Previous.e * FlankerRep * Trial.begin + (1|Subject), data = dat.use)
summary(FlankerRep_Begin)
```
###Middle
```{r}
FlankerRep_Mid = lmer(RTdrop ~ Current.e * Previous.e * FlankerRep * Trial.middle + (1|Subject), data = dat.use)
summary(FlankerRep_Mid)
```
###End
```{r}
FlankerRep_End = lmer(RTdrop ~ Current.e * Previous.e * FlankerRep * Trial.end + (1|Subject), data = dat.use)
summary(FlankerRep_End)
```
###Breaking down the significant three-ways that occured at beginning and middle.
###At beginning.
###Without repetitions.
```{r}
FlankerRep_0 = lmer(RTdrop ~ Current.e * Previous.e * Trial.begin + (1|Subject), data = filter(dat.use, FlankerRep == 0))
summary(FlankerRep_0)
```
###Only repetitions.
```{r}
FlankerRep_1 = lmer(RTdrop ~ Current.e * Previous.e * Trial.begin + (1|Subject), data = filter(dat.use, FlankerRep == 1))
summary(FlankerRep_1)
```
###At middle. 
###Without repetitions.
```{r}
FlankerRep_0 = lmer(RTdrop ~ Current.e * Previous.e * Trial.middle + (1|Subject), data = filter(dat.use, FlankerRep == 0))
summary(FlankerRep_0)
```
###Only repetitions.
```{r}
FlankerRep_1 = lmer(RTdrop ~ Current.e * Previous.e * Trial.middle + (1|Subject), data = filter(dat.use, FlankerRep == 1))
summary(FlankerRep_1)
```





